### 2015-02-22 fundamentals/impl.tex
reduced some extra wordiness. it's important information, but likely too far into the weeds

>>>>

In large simulations, many material objects may change frequently.  Material
decay can also contribute significantly to such changes.  In order to help
avoid unnecessary runtime performance and database size impacts, compositions
in \Cyclus have some special features.  In particular, compositions are stored
immutably in the database so that multiple material objects can hold references
to the same composition safely.  Additionally, when transmutation and decay
result in new compositions, those are cached for additional avoidance of
redundancy.Composition immutability in concert with decay history caching help
eliminate many redundant decay calculations in addition to reducing the total
number of composition objects recorded in the database.
\TODO{do we want a diagram helping show this composition caching?}
